Model-free and Bayesian Ensembling Model-based Deep Reinforcement Learning for Particle Accelerator Control Demonstrated on the FERMI FEL

### 2025-12-29 paper/main.tex
docs: Clarify anchored ensembling in paper, update README abstract wording, image paths, and table formatting.

	By employing an ensemble of networks and introducing noise to the regularization term's targets, a distribution of MAP solutions \cite{Gu2007, Chen2011, Bardsley2012, Pearce2018} is obtained, which mimics the true posterior.\\

>>>>

	By employing an ensemble of networks and introducing noise to the regularization term's targets, a distribution of MAP solutions \cite{Gu2007, Chen2011, Bardsley2012, Pearce2018} is obtained, which mimics the true posterior. This approach addresses a key criticism of standard deep ensembles: that randomly initialized networks merely find diverse local optima rather than sampling from the true posterior distribution. The regularization term anchoring the weights to a prior draw provides the theoretical linkage to Bayesian inference that standard ensembles lack.\\
